Why do we Eval?\\\Large A large-scale study of Eval usage in R

### 2021-03-09 paper/main.tex
Discussion for usage metrics

\paragraph{Discussion}

@@

\begin{itemize}
\item Figure 7: check that element counts are correct
\item Check that the percentage of operations performed within
  an \eval (5\%) is correct. That feels surprising to me.
\item I am having second thoughts about keeping the \c{ggplot2} data
  -- it is a big outlier that skews all the graphs...
\item Add a ``Discussion'' paragraph at the end that sums up the
  observations
\end{itemize}

>>>>

\paragraph{Discussion} \emph{Base} is more akin to use \eval for metaprogramming, \emph{kaggle} to evaluate parsed strings, and CRAN is dominated by symbol evaluation. In terms of number of calls, a few calls dominate, with a call from \emph{ggplot} being prominent in the CRAN corpus. When looking at the \eval sites, \eval is more spread out. These two measures emphasize two different points of view:

\begin{itemize}
	\item The number of calls is relevant to an optimizing compiler: the most frequent calls are the ones to be optimized first.
	\item The number of sites is relevant to the programmer/user: it describes better how programmers use \eval.
\end{itemize}

% What about a threat model?

@@

\begin{itemize}
\item Figure 7: check that element counts are correct
\item Check that the percentage of operations performed within
  an \eval (5\%) is correct. That feels surprising to me.
\end{itemize}
